### 2016-05-05 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Updated times and HRRs for gas burner report

\begin{table}[!ht]
\caption{Calculated Heat Release Rate for East Structure Tests}
% \begin{tabular}{lccccc}
%  \toprule
%  					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
% \textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
% 					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
% 					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
% 					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
% 					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
%  \midrule
% Test 2 				& 360 & 690	& 950 & 680 & 350 \\
% Test 3				& 360 & 690	& 950 & 680 & 350 \\
% Test 4				& 360 & 690	& 950 & 680 & 350 \\
% Test 5 - Seq. 1		& 360 & 690	& 950 & 680 & 350 \\
% Test 5 - Seq. 2		& 360 & 690	& 950 & 680 & 350 \\
% Test 5 - Seq. 3		& 360 & 690	& 950 & 680 & 350 \\
% Test 6 - Seq. 1		& 360 & 690	& 950 & 680 & 350 \\
% Test 6 - Seq. 2		& 360 & 690	& 950 & 680 & 350 \\
% Test 6 - Seq. 3		& 360 & 690	& 950 & 680 & 350 \\
\begin{tabular}{lc}
 \toprule
\textbf{Test}  		& 	\textbf{Heat Release Rate (kW)} \\
\midrule
Test 2 				& 			\\
Test 3				& 			\\
Test 4				& 	949		\\
Test 5 - Seq. 1		&  	723		\\
Test 5 - Seq. 2		&  	728		\\
Test 5 - Seq. 3		&  	724	    \\
Test 6 - Seq. 1		&  	718	    \\
Test 6 - Seq. 2		&   714     \\
Test 6 - Seq. 3		&   716	 	\\
\bottomrule
\end{tabular}
\label{table:HRR_East}
\end{table}

@@

\begin{table}[!ht]
\caption{Calculated Heat Release Rate for West Structure Tests}
\begin{tabular}{lc}
 \toprule
\textbf{Test}  			& 	\begin{tabular}{c} \textbf{Heat Release Rate} \\ \textbf{(kW)} \end{tabular} \\
\midrule
Test 22 				& 	756		\\
Test 23					& 	788		\\
Test 24					& 	784		\\
Test 25					&  	785		\\
\bottomrule
\end{tabular}
\label{table:HRR_West}
\end{table}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}[b]{cc}
 	\toprule
 	\textbf{Number} & \textbf{Event Description} \\
 	\midrule
 	1-3  & Burners ignited \\
 	4	 & 2nd floor west double door opened \\
 	5 	 & 1st floor west double door opened \\
 	6	 & 1st floor east double door opened \\
 	7 	 & 2nd floor east double door opened \\
 	8-10  & Burners extinguished \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Test Series 22 layout and sequence of events.}
\label{fig:west_test_22}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}[b]{cc}
 	\toprule
 	\textbf{Number} & \textbf{Event Description} \\
 	\midrule
 	1-3  & Burners ignited \\
 	4	 & Interior stairwell door opened \\
 	5 	 & 1st floor west double door opened \\
 	6	 & 2nd floor west double door opened \\
 	7 	 & 2nd floor south exterior door opened \\
 	8-10 & Burners extinguished \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Test Series 24 layout and sequence of events.}
\label{fig:west_test_24}
\end{figure}
\FloatBarrier

>>>>

\begin{table}[!ht]
\caption{Calculated Heat Release Rate for East Structure Tests}
\begin{tabular}{lccccc}
 \toprule
 					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
 \midrule
Test 2 				& 338 & 651	& 894 & 634 & 330 \\
Test 3				& 326 & 650	& 899 & 631 & 326 \\
Test 4				& 351 & 654	& 902 & 652 & 337 \\
Test 5 - Seq. 1		& 263 & 526	& 723 & 486 & 263 \\
Test 5 - Seq. 2		& 225 & 526	& 727 & 526 & 316 \\
Test 5 - Seq. 3		& 263 & 526	& 722 & 526 & 263 \\
Test 6 - Seq. 1		& 263 & 526	& 722 & 526 & 263 \\
Test 6 - Seq. 2		& 225 & 526	& 718 & 526 & 287 \\
Test 6 - Seq. 3		& 263 & 526	& 714 & N/A & N/A \\
% \begin{tabular}{lc}
%  \toprule
% \textbf{Test}  		& 	\textbf{Heat Release Rate (kW)} \\
% \midrule
% Test 2 				& 			\\
% Test 3				& 			\\
% Test 4				& 	949		\\
% Test 5 - Seq. 1		&  	723		\\
% Test 5 - Seq. 2		&  	728		\\
% Test 5 - Seq. 3		&  	724	    \\
% Test 6 - Seq. 1		&  	718	    \\
% Test 6 - Seq. 2		&   714     \\
% Test 6 - Seq. 3		&   716	 	\\
\bottomrule
\end{tabular}
\label{table:HRR_East}
\end{table}

@@

\begin{table}[!ht]
\caption{Calculated Heat Release Rate for West Structure Tests}
% \begin{tabular}{lc}
%  \toprule
% \textbf{Test}  			& 	\begin{tabular}{c} \textbf{Heat Release Rate} \\ \textbf{(kW)} \end{tabular} \\
% \midrule
% Test 22 				& 	756		\\
% Test 23					& 	788		\\
% Test 24					& 	784		\\
% Test 25					&  	785		\\
\begin{tabular}{lccc}
 \toprule
 					& 	\multicolumn{3}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		& 	1 Burner On 	& 	2 Burners On 	& 	3 Burners On \\
 \midrule
Test 22				& 	  287		 	&      316			&     	759 	  \\
Test 23				& 	  395		 	&      526			&     	788 	  \\
Test 24				& 	  287		 	&      631			&     	787 	  \\
Test 25				& 	  316		 	&      526			&     	785 	  \\
\bottomrule
\end{tabular}
\label{table:HRR_West}
\end{table}

\begin{figure}[!ht]
% \begin{minipage}[b]{0.8\columnwidth}
% 	\begin{flushleft}
% 	\small
% 	\begin{tabular}[b]{cc}
%  	\toprule
%  	\textbf{Number} & \textbf{Event Description} \\
%  	\midrule
%  	1-3  & Burners ignited \\
%  	4	 & 2nd floor west double door opened \\
%  	5 	 & 1st floor west double door opened \\
%  	6	 & 1st floor east double door opened \\
%  	7 	 & 2nd floor east double door opened \\
%  	8-10  & Burners extinguished \\
% 	\bottomrule
% 	\end{tabular}
% 	\end{flushleft}
% \end{minipage}
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{\normalsize Event Times (mm:ss) for Test Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 		& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	(1) Corner burner on 					& 	9:05 			&	 3:45		\\
	(2) Middle burner on 					&   8:45	  		&	 3:55		\\
	(3) Center burner on 					&   8:15	  		&	 4:04		\\
	(4) 2nd floor west double door opened 	&   11:30	  		&    6:00		\\
	(5) 1st floor west double door opened 	&	13:30	  		&    8:02 	 	\\
	(6) 1st floor east double door opened 	&   15:45		  	&    10:00		\\
	(7) 2nd floor east double door opened	&   18:00		  	&    12:08		\\
	(8) PPV fan on 							&   19:10		  	&    14:01		\\
	(9) PPV fan off              			&   21:34		  	&    16:30		\\
	(8) Center burner off 					&   22:00		  	&    17:00		\\
	(9) Middle burner off 					&   22:00		  	&    17:00		\\
	(10) Corner burner off 					&   22:00		  	&    17:00		\\
	% doors were opened, fan was on after burners turned off
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Test Series 22 layout and sequence of events.}
\label{fig:west_test_22}
\end{figure}

\begin{figure}[!ht]
% \begin{minipage}[b]{0.8\columnwidth}
% 	\begin{flushleft}
% 	\small
% 	\begin{tabular}[b]{cc}
%  	\toprule
%  	\textbf{Number} & \textbf{Event Description} \\
%  	\midrule
%  	1-3  & Burners ignited \\
%  	4	 & Interior stairwell door opened \\
%  	5 	 & 1st floor west double door opened \\
%  	6	 & 2nd floor west double door opened \\
%  	7 	 & 2nd floor south exterior door opened \\
%  	8-10 & Burners extinguished \\
% 	\bottomrule
% 	\end{tabular}
% 	\end{flushleft}
% \end{minipage}
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{\normalsize Event Times (mm:ss) for Test Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	(1) Corner burner on 						& 	2:30 			&	 2:00		\\
	(2) Middle burner on 						&   2:45	  		&	 2:00		\\
	(3) Center burner on 						&   3:00	  		&	 2:00		\\
	(4) Interior stairwell door opened 			&   5:00	  		&    4:00		\\
	(5) 1st floor west double door opened 		&	7:00	  		&    6:11 	 	\\
	(6) 2nd floor west double door opened 		&   9:00		  	&    8:00		\\
	(7) 2nd floor south exterior door opened	&   11:00		  	&    10:00		\\
	(8) PPV fan on 								&   13:00		  	&    12:00 		\\
	% (9) PPV fan off              				&   16:30		  	&    		\\
	(8) Center burner off 						&   15:00		  	&    14:00		\\
	(9) Middle burner off 						&   15:00		  	&    14:00		\\
	(10) Corner burner off 						&   15:00		  	&    14:00		\\
	% doors were opened, fan was on after burners turned off
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Test Series 24 layout and sequence of events.}
\label{fig:west_test_24}
\end{figure}
\FloatBarrier
